MaBoSS for HPC environments: Implementations of the continuous time Boolean model simulator for large CPU clusters and GPU accelerators

### 2024-03-22 Article.tex
update

\papercat{Paper}

@@

The source code of the proposed implementations is publicly available at their respective GitHub repositories\footnote{\url{https://github.com/sysbio-curie/MaBoSS.GPU}} \footnote{\url{https://github.com/sysbio-curie/MaBoSS-env-2.0}}. We also provide the scripts, presented plots, data and instructions to reproduce the benchmarks in the replication package\footnote{\url{https://github.com/asmelko/gigascience24-artifact}}.

@@

>>>>

\papercat{Technical Note}

@@

The source code of the proposed implementations is publicly available at their respective GitHub repositories\footnote{\url{https://github.com/sysbio-curie/MaBoSS.GPU}} \footnote{\url{https://github.com/sysbio-curie/MaBoSS-env-2.0}}. We also provide the scripts, presented plots, data and instructions to reproduce the benchmarks in the replication package\footnote{\url{https://github.com/sysbio-curie/gigascience24-artifact}}.

@@

\section{Availability of source code and requirements}
% flex and bison are linux only :/
\begin{itemize}
	\item Project name: MaBoSS.GPU
	\item Project home page: \url{https://github.com/sysbio-curie/MaBoSS.GPU}
	\item Operating system(s): Platform independent
	\item Programming language: C++, CUDA
	\item Other requirements: Flex, Bison, CMake >= 3.18, Cuda toolkit >= 12.0
	\item License: MIT
\end{itemize}

\begin{itemize}
	\item Project name: MaBoSS.MPI
	\item Project home page: \url{https://github.com/sysbio-curie/MaBoSS}
	\item Operating system(s): Platform independent
	\item Programming language: C++
	\item Other requirements: Flex, Bison
	\item License: BSD3-clause
\end{itemize}

\section{Data availability}
The scripts, presented plots, data and instructions to reproduce the benchmarks are available on GitHub~\cite{adam_smelko_2024_10841007}.

\subsection{Competing Interests}
The authors declare that they have no competing interests.
